Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2023-07-17 ba_resubmit/response_to_reviewers2.tex

Thank you for the thoughtful feedback. We have made several broad changes to address the Associate Editor's overall critiques, and have addressed each specific comment from the reviewer.

\section{AE Comments}

\pointRaised{AE}{I must add that reading the paper still feels like a chore, in part because the notation is so heavy, which may be hard to avoid, but also, in part, because some wording choices make certain sentences hard to parse, which can certainly be improved.}

\textcolor{teal}{Suggestion: Write a strong paragraph to the Editor after the paper is finalized. Come back to this. Explain that we have tried to simplify the notation when possible, however, in some places, the heavy notation is not possible. Thus, we have worked on improving more precise wording and removing sections or wording that is distracting or not needed. Thank the Editor and Associate Editor for helping us improve upon what we believe to be an important paper and breakthrough in the literature.}

\textcolor{teal}{I would not make a large list of all the notation we have changed as it may cause the Editor to go picking over the paper more.}x

@@

	\item In Section 4.1, we have provided a specific example of a comparison vector and how the hashing procedure works.

	\item Section 4.1 introduces the summary statistic $N_{j_p}$. After careful review, we realized that by changing the order of subscripts and instead using $N_{p_j}$, we can replace the sum of counts across all records (previously denoted $H_p$), with the more intuitive $N_p$. Thus, we have removed all of the ''$H$" quantities throughout Section 4. 
\end{itemize}
}

\pointRaised{AE}{Line 80 on p. 3 says: “For ease of readability, we follow the convention established by Sadinle (2017) and say “record $i \in X_1$” rather than the more compact $x_{1i}$.” Taking this at face value implies that, in any sentence, one could swap “record $i \in X_1$” for “$x_{1i}$,” which clearly is not true.  So, as it stands, the sentence does little to improve ease of readability.  In fact, if the point is that “$x_{1i}$” will never be used again, why is the notation introduced in the first place?}

\textcolor{teal}{Thank the Editor, explain the change. I have removed repetition and shortened this bit.}

\reply{
%We added this sentence in an attempt to address a previous reviewer comment pointing out a conflation between the record itself and the index directing towards that record.
\textcolor{teal}{We thank the Editor for bringing up this point. In order to simplify notation, we refer to the two data files as} 
 $A$ and $B$, where the updated material reads:

@@

	\pointRaised{R}{%
	For the missing data treatment now included just before Section 2.1, is the assumption truly missing at random, or missing completely at random? Or, does this distinction not matter because of the independence assumed across elements of the comparison vector?}

	\reply{% 
		The assumption is missing completely at random. You are correct that this is a result of the independence assumed across elements of the comparison vector. This has been clarified.
	}

	\pointRaised{R}{%
	Appendix 8.2: I appreciate the streamlining of the discussion of the proposed algorithms and think it was a good choice to move the full derivation to an appendix. However, I do not follow the re-expression of the pmf for $\Gamma_{.j}$. First, the opening square brackets are still misplaced
	throughout. In the second line of this derivation, the authors divide the expression by a product of the element-wise conditional probabilities of a match in the comparison vector (u), raised by an indicator that the element of the comparison vector equals a particular value. Perhaps I misunderstand, but I believe this product is not constant in $\Gamma_{.j}$ or $u$, and so the total expression is not proportional to the line above, as interpreted as a pmf. I think that the end effect is that the last line of the newly expressed pmf is missing a factor of $\prod_i \prod_f \prod_l u_{fl}^{I(\gamma_{ij}^f = l) I_{obs}(\gamma_{ij}^f)}$ regardless of the value of $z_j$.}

\textcolor{teal}{Don't apologize!}

\reply{%
	\textcolor{teal}{The square brackets have been corrected. We have clarified the derivation of the full conditional distribution of $Z_j$, separately handling the case when $B_j$ has a match and when it does not. }
}

@@

\reply{%
	The square brackets have been corrected, and we apologize for the oversight. We have clarified derivation of the likelihood for $Z_j$, separately handling the case when $B_j$ has a match and when it does not.
}

	\pointRaised{R}{%
Appendix 8.2: Thank you for including the details on integrating out pi from the full conditionals. They surprised me. I had assumed that the authors had integrated out pi in the prior for Z, as this is what Sadinle (2017) had done to form the “beta prior for bipartite matchings”. (1) Does the alternate approach presented in this paper provide a different algorithm than directly integrating the prior distribution? (2) Is the presented alternative approach justified?}

\textcolor{teal}{Brian: I think it's very important that we answer this carefully and in a strong manner. See below. Note: The edits in Appendix 8.2 regarding the justification that I wrote have been removed.}

\textcolor{teal}{No, we do not integrate out $\pi$ as done in Sadinle as this would result in a sequential sampler as opposed to the parallel one that we propose. This is one of our contributions to our paper. (1) Yes, our alternative approach is different than directly integrating over the prior distribution. We have attempted to make this more clear in our revised version. In short, our prior distribution over $Z$ leads to a Gibbs sampler that leads to parallel updates, which contrasts that of Sadinle (2018). Of course, we could integrate out $\pi$ in our approach, however, this would lead to sequential updates, which would be slow in practice. (2) Yes, our alternative approach is justified. We provide a justification in Appendix 8.2 regarding why the updates are independent and not sequential. Thank you for the excellent questions, which have greatly improved our paper. }

%
%\reply{%
%	We realize that the integration of pi out of the full conditionals is not necessary for our sampler. For clarity, we decided to redo the simulations using a Gibbs sampler that samples $\pi$ from its full conditional, and then samples $Z$ from its full conditionals. We obtained equivalent results, which is unsurprising, because with high numbers of observations, the posterior of the beta distribution is highly concentrated around its mean.
%	
%	Therefore, we have updated the paper with full conditionals for the standard Gibbs sampler. We leave the remark about marginalization in the Appendix to facilitate comparisons to Sadinle's method.
%
%}

### 2023-07-17 ba_resubmit/kundinger_resubmit2.tex
add in clarification to AE regarding parallel versus sequential updates in appendix 8.2 for brian to look at.

>>>>

\textcolor{blue}{Observe that the full conditional in (\ref{eqn:z_full_conditional2}) does not depend on $\bm{Z}^{(s)},$ implying that 
\begin{align}
p(\bm{Z}^{(s+1)} \mid \gamma, \bm{m}^{(s+1)}, \bm{u}^{(s+1)}, \pi) \propto \prod_q \left(\prod_j
p\left(Z_j^{(s+1)}  = q \mid \gamma, \bm{m}^{(s+1)}, \bm{u}^{(s+1)}, \pi \right)
\right).
\end{align}
Therefore, we update the full conditional for $\bm{Z}^{(s+1)}$ in parallel. This contrasts the Gibbs sampler of  \cite{sadinle_bayesian_2017}, where the update to the matching matrix is sequential and accomplished using a partially collapsed Gibbs sampler, where one integrates out $\pi.$ We do not opt for this approach as it would lead to similar sequential updates, which are computationally slow.}
